%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Gabriel Lando}} & \href{mailto:mail@gabriellando.com}{mail@gabriellando.com} \\
  {Expert Software Engineer | Backend \& Cloud Systems} & \href{https://www.gabriellando.com}{gabriellando.com} \\
  {} & \href{https://github.com/gabriel-lando}{github.com/gabriel-lando} \\
  {} & \href{https://www.linkedin.com/in/gabriellando}{linkedin.com/in/gabriellando}
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Software Applications Engineer (Expert)}{2025 -- Present}
    {HP Inc.}{Porto Alegre, Brazil}
    \begin{itemize}
      \item Acting as technical lead for the \textit{HP Remote System Controller}, defining backend architecture and guiding implementation of embedded and system-level components.
      \item Leading architectural decisions and system design for scalable and reliable backend services.
      \item Establishing and enforcing engineering best practices, including modular architecture, automated testing, and system observability.
    \end{itemize}

  \resumeSubheading
    {Software Applications Engineer (Specialist)}{2023 -- 2024}
    {HP Inc.}{Porto Alegre, Brazil}
    \begin{itemize}
      \item Played a key role in the early development of the \textit{HP AI Companion}, leading backend architecture and driving core system design decisions to deliver \textbf{production-grade AI features}.
      \item Acted as technical lead across external and cross-functional projects, driving architectural alignment and technical execution.
      \item Designed and maintained CI/CD pipelines and cloud-native infrastructure using Docker and Kubernetes.
    \end{itemize}

  \resumeSubheading
    {Software Applications Engineer (Intermediate)}{2021 -- 2023}
    {HP Inc.}{Porto Alegre, Brazil}
    \begin{itemize}
      \item Developed kernel-level drivers for virtualized components, improving system performance and resource utilization.
      \item Built and maintained DevOps infrastructure and CI/CD pipelines supporting scalable deployments.
      \item Contributed to research and development initiatives, prototyping and validating new technologies.
      \item Built integrations between high-performance C/C++ components and modern application layers (DirectShow, Media Foundation).
    \end{itemize}

  \resumeSubheading
    {Software Applications Engineer (Entry)}{2021}
    {HP Inc.}{Porto Alegre, Brazil}
    \begin{itemize}
      \item Supported development and maintenance of software components within a global engineering team.
      \item Contributed to debugging, testing, and incremental feature development across multiple projects.
    \end{itemize}

  \resumeSubheading
    {Research and Development Intern}{2019 -- 2021}
    {HP Inc.}{Porto Alegre, Brazil}
    \begin{itemize}
      \item Built and validated proof-of-concept solutions in collaboration with global cross-functional teams.
      \item Developed backend components and prototypes across multiple technology stacks, supporting rapid experimentation and deployment.
    \end{itemize}

  \resumeSubheading
    {Undergraduate Research Scholar}{2017 -- 2019}
    {Universidade Federal do Rio Grande do Sul (UFRGS)}{Porto Alegre, Brazil}
    \begin{itemize}
      \item Contributed to the Brazil--EU FUTEBOL-ICT research project focused on IoT and wireless communication.
      \item Developed solutions using programmable radios (USRP) and maintained LTE networks with srsLTE.
      \item Managed and maintained research testbed infrastructure.
    \end{itemize}

\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart

  \resumeSubheading
    {Master's Degree in Computer Science}{2025 -- Present}
    {PPGC -- Universidade Federal do Rio Grande do Sul (UFRGS)}{Porto Alegre, Brazil}
    \begin{itemize}
      \item Research focus on low-level Software-Defined Radio (SDR) systems and signal processing.
    \end{itemize}

  \resumeSubheading
    {Bachelor of Computer Engineering}{2017 -- 2022}
    {Universidade Federal do Rio Grande do Sul (UFRGS)}{Porto Alegre, Brazil}

\resumeSubHeadingListEnd


%-----------PUBLICATIONS-----------------
\section{Publications}
\resumeSubHeadingListStart
  \item \textit{Evaluating the Performance of Open Source Software Implementations of the 5G Network Core}
  \item \textit{Enabling Cloud-Native Observability for White-Box Performance Analysis of the 5G Core}
  \item \textit{Explainable Performance Analysis of Open-Source 5G Core Network Implementations via Observability}
  \item \textit{Optical and Wireless Network Convergence in 5G Systems -- An Experimental Approach}
\resumeSubHeadingListEnd

%-----------PATENTS-----------------
\section{Patents (HP Inc.)}
\resumeSubHeadingListStart
  \item Image Adjustment
  \item Port Notifications
  \item Remote Universal Serial Bus Manager
  \item Light Intensity Determination
  \item Conveying Aggregate Psychological States of Multiple Individuals
  \item Inferring Psychological State
  \item Training Data Collection During Data Collection-Unposed Sessions
\resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Skills}
\resumeSubHeadingListStart
  \item \textbf{Programming Languages}{: Python, C, C++, C\#, JavaScript/Node.js, Go, Bash, PowerShell}
  \item \textbf{Cloud \& Infrastructure}{: Docker, Kubernetes, CI/CD, Git, Cloud Native Architecture, Infrastructure Automation, Cloud Computing (AWS), Virtualization, Linux, Windows}
  \item \textbf{Backend \& AI}{: System Design, API Development, Distributed Systems, AI/LLM Integration, RAG Architecture, Observability}
  \item \textbf{Databases \& Storage}{: PostgreSQL, MySQL, MongoDB, DynamoDB, Data Modeling, Query Optimization}
  \item \textbf{Systems \& Media}{: Embedded Systems, Systems Programming, Windows Kernel/Driver Development, DirectShow, Media Foundation, Audio/Video Processing}
  \item \textbf{Networking \& Hardware}{: Network Architecture, VLAN \& Firewalls, SDR, LTE/5G Networking, IoT Prototyping, PCB \& Firmware Development}
  \item \textbf{Core Skills}{: Technical Leadership, Software Architecture, Software Research and Development, Troubleshooting}
  \item \textbf{Soft Skills}{: High reliability, strong analytical and investigative mindset, advanced inductive and deductive reasoning, self-directed learner, effective conflict resolution and collaboration}
  \item \textbf{Languages}{: Portuguese (Native), English (Full Professional)}
\resumeSubHeadingListEnd

%-----------TECHNICAL PROJECTS-----------------
\section{Technical Projects}
\resumeSubHeadingListStart

  \resumeSubheading
    {Personal Homelab Infrastructure}{}
    {Self-Hosted Environment}{}
    \begin{itemize}
      \item Architected and maintain a multi-service homelab with virtualized workloads and containerized applications.
      \item Designed network topology with VLAN segmentation, firewall policies, and inter-VLAN routing.
      \item Deployed and administer production-grade Linux servers and self-hosted services.
    \end{itemize}

  \resumeSubheading
    {Embedded and Hardware Development}{}
    {Personal Projects}{}
    \begin{itemize}
      \item Developed embedded firmware on microcontrollers for low-level, hardware-proximate applications.
      \item Designed and fabricated custom PCBs for specialized electronic solutions.
      \item Integrated hardware, firmware, and software layers for end-to-end functional prototypes.
    \end{itemize}

  \resumeSubheading
    {Digital Fabrication and Prototyping}{}
    {Personal Projects}{}
    \begin{itemize}
      \item Leveraged 3D printing for rapid mechanical prototyping and precision hardware enclosures.
      \item Executed iterative design cycles combining electronics, firmware, and mechanical components.
    \end{itemize}

\resumeSubHeadingListEnd


\end{document}